---
title: "Density Calculations"
output: html_document
author: Mandy Liesch
date: "2025-02-19"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

#set the working directory here
setwd("/Desktop/MissouriGCAM")

```


The objective of this code is to provide the processing of raw input files in the GCAM model to calculate the area, vegetative and soil emissions, as well as the overall vegetative soil and carbon density as a followup to the GCAM Soil Carbon Meeting with PNNL on 2/18/25.

## Load Packages and Files 

```{r}
library(tidyverse)
library(ggpubr)

#Load the vegetative carbon emissions
NEW_AG_Missouri_Emissions <- read_csv("NEW_AG_Missouri_Emissions.csv")

#load the land use history file
newFullHist<-read_csv("fullHistory.csv")

#Input my soil series
FAO_soil <- read_csv("MissouriR_s84_soil_luc_data.csv")

```

## Load the Custom Color Pallettes 

```{r}
LUColors <- c("UrbanLand"="#C80813FF", "Tundra"="#71D0F5FF", 
              "Rock/Ice/Desert"="#8A9197FF", "Cropland" = "#FED439FF",
              "HarvCropLand"="#FED439FF", "OtherArableLand" = "#D2AF81FF", 
              "Pasture"= "#FD8CC1FF", "UnmanagedPasture"="#370335FF", 
              "Grassland" = "#46732EFF", "Forest" = "#075149FF", 
              "Shrubland" = "#F05C3BFF", "otherNotArable"="#8A9197FF")

# Vegetative Based Color Pallet
vegCEmissions<-c("#46732EFF")
```


## Land Use Preprocessing

```{r}
#Do a final reclassification with the new forest definition
newFullName<- newFullHist %>% 
  mutate(LandUse = case_when(
    Category == "HarvCropLand" ~ "HarvCropLand",
    Category == "OtherArableLand" ~"OtherArableLand",
    Category %in% c("Forest", "UnmanagedForest")~ "Forest",
    Category =="Grassland" ~ "Grassland", 
    Category=="Pasture" ~ "Pasture",
    Category=="UnmanagedPasture"~ "UnmanagedPasture",
    Category=="Shrubland" ~ "Shrubland",
    Category=="Tundra" ~ "Tundra",
    Category=="UrbanLand" ~ "UrbanLand"
  )
)

#Resummarize the values by the new land use categories
land_sum_cat_LU<-newFullName %>% 
  group_by(LandUse) %>% 
  #Sum everything that needs to happen
  summarise(across(where(is.numeric), sum)) %>%
  #remove all values with NA
  filter(complete.cases(.))
  

#Pivot the tables to the long values
newLongHist<- land_sum_cat_LU %>% 
  pivot_longer(!c(LandUse), names_to="year", values_to = "area") %>%
  #Rename the column to category
  rename(Category = LandUse)
```

## Vegetative Emissions Preprocessing 

```{r}
#Break up the land leaf columns into subsets 
#(each land leaf has 4 different categories)
NA_MO_Veg<-NEW_AG_Missouri_Emissions%>% 
  separate(LandLeaf, c("LandUse", "Basin", "Water", "Input"))

#Sum together all of the land leaf files by land use t+ype
sum_NA_MO_Veg<- NA_MO_Veg %>% 
  group_by(LandUse) %>% 
  summarise(across(where(is.numeric), sum))

#Reclassify land use types into broader categories
veg_cat_LU<-sum_NA_MO_Veg %>% mutate(Category = case_when(
  #Cropland category  
  LandUse %in% 
    #Biomass Crops
    c("biomassGrass", "biomassTree",  
    #Fodder Crops
      "FodderGrass", "FodderHerb", 
    #Grain Crops
      "Corn",  "Soybean", "Wheat", "OtherGrain",
    #Oil Crops
      "OilCrop", "Rapeseed", 
    #Other Crops
      "FiberCrop", "MiscCrop", "RootTuber",  "SugarCrop") 
    #Land Use Name
      ~ "HarvCropLand",
    #Other Arable Land
    LandUse == "OtherArableLand" ~"OtherArableLand",
    #Forest categories
    LandUse %in% c("Forest", "UnmanagedForest", "ProtectedUnmanagedForest")
                ~ "Forest",
    #Grassland categories
    LandUse %in% c("Grassland", "ProtectedGrassland") ~ "Grassland", 
    #Pasture category
    LandUse=="Pasture" ~ "Pasture",
    #Unamanged pasture category
    LandUse %in% c("ProtectedUnmanagedPasture", "UnmanagedPasture") 
              ~ "UnmanagedPasture",
    #Shrubland category
    LandUse %in% c("Shrubland", "ProtectedShrubland") ~ "Shrubland",
    #Other categories
    LandUse=="Tundra" ~ "Tundra",
    LandUse=="UrbanLand" ~ "UrbanLand",
    #Default Return Statement
    TRUE~NA_character_
  )
)

#Sum everything up by defined land use category
veg_sum_cat_LU<-veg_cat_LU %>% 
  group_by(Category) %>% 
  summarise(across(where(is.numeric), sum))

#Create a long dataframe with land use, years, and emissions rate
veg_long_sum_LU<-veg_sum_cat_LU %>% 
  pivot_longer(!c(Category), names_to="year", values_to = "emissions") %>%
  #convert years into the numeric values
  mutate(year = as.numeric(year))

#Add the area "Area (thous km2)", to the emissions in (Mt CO2 Equiv/Year)
new_veg<-merge(newLongHist, veg_long_sum_LU, all=TRUE)

#Filter out the years required
new_veg_filter<- new_veg %>% 
  filter(year>= '1705'&year<='2060') %>%
  #multiply emissions by 1000
  mutate(kg = emissions*1000) %>%
  #calculate density 
  mutate(density =kg/area) %>%
  #convert years into the numeric values
  mutate(year = as.numeric(year)) #%>%
  #filter out to the desired land use choice from above 

  #CAUTION, if you do these options, the individual values wont reflect the name 
  # correctly in the graphs. Look above for the other land use categories
  
  #filter(Category == 'Grassland')
  #filter(Category == 'Pasture')
  #filter(Category == 'OtherArableLand')



```


## Land and Vegetation Plots

```{r}
#Create a spaghetti plot of land use area using area by category
landUseLines.plt<-ggplot(data= new_veg_filter, 
                         aes(x=year, y=area, group=Category))+
  geom_line(aes(color=Category), size=2) +
  #add a title
  ggtitle("A) Historic and Future Area by Land Use Type") +
  #add labels
  labs( x='Year', y='Land Area (thous sq km)') +
  #use the custom color pallette
  scale_color_manual(values=LUColors) +
  #Fix the x scale and labels
  scale_x_continuous(breaks=c(1700,1750,1800,1850,1900,1950,2000,2050), 
                     labels = c("1700","1750","1800","1850","1900","1950",
                                "2000","2050")) +
  #Add the vertical lines
  geom_vline(xintercept = c(1850, 1950, 1990, 2015)) +
  #remove the legend
  theme(legend.position = "none")


#Calculate vegetative emissions graph by land use
vegEmissLU.plt<-ggplot(data= new_veg_filter, aes(x=year, y=emissions, 
                                              group=Category, color=Category))+
  geom_line(size=2) +
  #Add the titles 
  ggtitle("B) Historic and Future Vegetative Emissions by Land Use Type") +
  #Add the labels
  labs( x='Year', y='Annual Emissions (Mt/year)') + 
  #Utilize the custom color scale and create the labels and spacing for 
  #words in the legend
  scale_color_manual(values=LUColors, name = "Land Use", 
                     labels = c( "Forest", "Grassland", "Harvested Cropland", 
                                 "Other Arable Land", "Pasture", "Shrubland", 
                                 "Tundra", "Unmanaged Pasture", "Urban Land")) +
  #scale and label the x axis breaks
  scale_x_continuous(breaks=c(1700,1750,1800,1850,1900,1950,2000,2050), 
                     labels = c("1700","1750","1800","1850","1900","1950",
                                "2000","2050")) +
  #add the vertical lines
  geom_vline(xintercept = c(1850, 1950, 1990, 2015)) +
  #add the legend at the bottom
  theme(legend.position = "none")

#create the density plots for land use by year
vegDensity.plt<-ggplot(data= new_veg_filter, aes(x=year, y=density, 
                                         group=Category, color=Category))+
  geom_line(size=2) +
  #add a title
  ggtitle("C. Historic and Future Vegetative Emissions Rate of Change by Land Use Type") +
  #add labels
  labs( x='Year', y='Annualized Density (kg/thous sq km/Year)') +
  #use custom color and labels 
  scale_color_manual(values=LUColors, name = "Land Use", 
                     labels = c( "Forest", "Grassland", "Harvested Cropland", 
                                 "Other Arable Land", "Pasture", "Shrubland", 
                                 "Tundra", "Unmanaged Pasture", "Urban Land")) +
  #customize the x axis breaks and labels
  scale_x_continuous(breaks=c(1700,1750,1800,1850,1900,1950,2000,2050), 
                     labels = c("1700","1750","1800","1850","1900","1950",
                                "2000","2050")) +
  #add the vertical lines
  geom_vline(xintercept = c(1850, 1950, 1990, 2015)) +
  #but the legend on the bottom
  theme(legend.position="bottom")



```

## Composite Vegetative Emissions and Density Graph

```{r}
compVegEmiss.plt<-ggarrange(landUseLines.plt, vegEmissLU.plt, vegDensity.plt,
          ncol = 1, nrow = 3,
          heights = c(2, 2, 3))

compVegEmiss.plt

```

## FAO Soil Data Preprocessing

```{r}

# Remove the extra columns
FAO_soil <- select(FAO_soil, -c(scenario, region))

#Separate the LandLeaf series into four columns
NA_MO_Soil<-FAO_soil%>% 
  separate(LandLeaf, c("LandUse", "Basin", "Water", "Input"))

#Sum by the soil type AND land uses
sum_NA_MO_Soil<- NA_MO_Soil %>% 
  group_by(LandUse) %>%
  summarise(across(where(is.numeric), sum))

#Recategorize the land use types into condensed categories
soil_cat_LU<-sum_NA_MO_Soil %>% 
  mutate(Category = case_when(
#Cropland category  
  LandUse %in% 
    #Biomass Crops
    c("biomassGrass", "biomassTree",  
    #Fodder Crops
      "FodderGrass", "FodderHerb", 
    #Grain Crops
      "Corn",  "Soybean", "Wheat", "OtherGrain",
    #Oil Crops
      "OilCrop", "Rapeseed", 
    #Other Crops
      "FiberCrop", "MiscCrop", "RootTuber",  "SugarCrop") 
    #Land Use Name
      ~ "HarvCropLand",
    #Other Arable Land
    LandUse == "OtherArableLand" ~"OtherArableLand",
    #Forest categories
    LandUse %in% c("Forest", "UnmanagedForest", "ProtectedUnmanagedForest")
                ~ "Forest",
    #Grassland categories
    LandUse %in% c("Grassland", "ProtectedGrassland") ~ "Grassland", 
    #Pasture category
    LandUse=="Pasture" ~ "Pasture",
    #Unamanged pasture category
    LandUse %in% c("ProtectedUnmanagedPasture", "UnmanagedPasture") 
              ~ "UnmanagedPasture",
    #Shrubland category
    LandUse %in% c("Shrubland", "ProtectedShrubland") ~ "Shrubland",
    #Other categories
    LandUse=="Tundra" ~ "Tundra",
    LandUse=="UrbanLand" ~ "UrbanLand",
    #Default Return Statement
    TRUE~NA_character_
  )
)

#Re-summarize by the newly defined categories
soil_sum_cat_LU<-soil_cat_LU %>% 
  group_by(Category) %>% 
  summarise(across(where(is.numeric), sum))

#Create the long values from the wide column
soil_long_sum_LU<-soil_sum_cat_LU %>% 
  pivot_longer(!c(Category), names_to="year", 
               values_to = "emissions") 


#Merge the land use variables to the soil values
new_soil<-merge(newLongHist, soil_long_sum_LU, all=TRUE)


new_soil_filter<- new_soil %>% 
  filter(year>= '1705'&year<='2060') %>%
  #multiply emissions by 1000
  mutate(kg = emissions*1000) %>%
  #calculate density 
  mutate(density =kg/area) %>%
  #convert the years to numeric
  mutate(year = as.numeric(year)) #%>%
  #filter out to the desired land use choice from above

  #CAUTION, if you do these options, the individual values wont reflect the name 
  # correctly in the graphs. Look above for the other land use categories

  #filter(Category == 'Grassland')
  #filter(Category == 'Pasture')
  #filter(Category == 'OtherArableLand')

```

## FAO Soil Emissions and Density Calculations

```{r}
#Create the FAO Soil Emissions Plots
soilEmissFAO.plt<-ggplot(data= new_soil_filter, aes(x=year, y=emissions, 
                                             group=Category, color=Category))+
  geom_line(size=2) +
  #Add the title
  ggtitle("FAO Glosis Emissions") +
  #Add labels
  labs( x='Year', y='Annual Emissions (Mt/year)') + 
  #Utilize the custom color scale and create the labels and spacing 
  #for the words in the legend
  scale_color_manual(values=LUColors, name = "Land Use", 
                     labels = c( "Forest", "Grassland", "Harvested Cropland", 
                                 "Other Arable Land", "Pasture", "Shrubland", 
                                 "Tundra", "Unmanaged Pasture", "Urban Land")) +
  #Scale and label the x axis
  scale_x_continuous(breaks=c(1700,1750,1800,1850,1900,1950,2000,2050), 
                     labels = c("1700","1750","1800","1850","1900","1950",
                                "2000","2050")) +
  #scale and label the y axis
  scale_y_continuous(breaks=c(-90, -60, -30, 0, 30, 60, 90)) +
  ylim(-110, 90) +
  #add vertical lines
  geom_vline(xintercept = c(1850, 1950, 1990, 2015)) +
  #remove the axis title and legend
  theme(axis.title.y = element_blank(),
    legend.position = "none") 
  

#create a density plot for FAO
soilDensFAO.plt<-ggplot(data= new_soil_filter, aes(x=year, y=density, 
                                       group=Category, color=Category))+
  geom_line(size=2) +
  #add title
  ggtitle("FAO Glosis Density") +
  #Utilize the custom color scale and create the labels and 
  #spacing for the words in the legend
  scale_color_manual(values=LUColors, name = "Land Use", 
                     labels = c( "Forest", "Grassland", "Harvested Cropland", 
                                 "Other Arable Land", "Pasture", "Shrubland", 
                                 "Tundra", "Unmanaged Pasture", "Urban Land")) +
  #add labels to the plot
  labs( x='Year', y='(kg/thous sq km/Year)') +
  #add the scale and labels for the x axis
  scale_x_continuous(breaks=c(1700,1750,1800,1850,1900,1950,2000,2050), 
                     labels = c("1700","1750","1800","1850","1900","1950",
                                "2000","2050")) +
  #add vertical lines
  geom_vline(xintercept = c(1850, 1950, 1990, 2015)) +
  theme(legend.position="bottom") 

```

```{r}
#Create the composite Emissions figure with Land Use, and emissions
compSoilEmiss.plt<-ggarrange(landUseLines.plt, soilEmissFAO.plt, soilDensFAO.plt, ncol = 1, nrow=3, heights = c(2, 2, 3))

compSoilEmiss.plt
```